---
title: "679_Data_cleaning"
output: pdf_document
date: "2024-04-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("data.table")
library(dplyr)
library(purrr)
library(survival)
library(dplyr)
library(tidyr)
```


# read files
```{r}
core_2018_0B11 <- read.csv("core_2018_0B11.csv")
core_2019_0B11 <- read.csv("core_2019_0B11.csv")

core_2018_0CTS <- read.csv("core_2018_0CTS.csv")
core_2019_0CTS <- read.csv("core_2019_0CTS.csv")
```

```{r}
# filter 2018 with 0b11
filter_0B11_core_2018 <- core_2018 %>% filter(grepl('^0B11', I10_PR1)|grepl('^0B11', I10_PR2)|grepl('^0B11', I10_PR3)|
                                      grepl('^0B11', I10_PR4)|
                                      grepl('^0B11', I10_PR5)|
                                      grepl('^0B11', I10_PR6)|
                                      grepl('^0B11', I10_PR7)|
                                      grepl('^0B11', I10_PR8)|
                                      grepl('^0B11', I10_PR9)|
                                      grepl('^0B11', I10_PR10)|
                                      grepl('^0B11', I10_PR11)|
                                      grepl('^0B11', I10_PR12)|
                                      grepl('^0B11', I10_PR13)|
                                      grepl('^0B11', I10_PR14)|
                                      grepl('^0B11', I10_PR15)|
                                      grepl('^0B11', I10_PR16)|
                                      grepl('^0B11', I10_PR17)|
                                      grepl('^0B11', I10_PR18)|
                                      grepl('^0B11', I10_PR19)|
                                      grepl('^0B11', I10_PR20)|
                                      grepl('^0B11', I10_PR21)|
                                      grepl('^0B11', I10_PR22)|
                                      grepl('^0B11', I10_PR23)|
                                      grepl('^0B11', I10_PR24)|
                                      grepl('^0B11', I10_PR25))
```

```{r}
# filter core 2018 with 0cts
filter_0CTS_core_2018 <- core_2018 %>% filter(grepl('^0CTS', I10_PR1)|grepl('^0CTS', I10_PR2)|grepl('^0CTS', I10_PR3)|
                                      grepl('^0CTS', I10_PR4)|
                                      grepl('^0CTS', I10_PR5)|
                                      grepl('^0CTS', I10_PR6)|
                                      grepl('^0CTS', I10_PR7)|
                                      grepl('^0CTS', I10_PR8)|
                                      grepl('^0CTS', I10_PR9)|
                                      grepl('^0CTS', I10_PR10)|
                                      grepl('^0CTS', I10_PR11)|
                                      grepl('^0CTS', I10_PR12)|
                                      grepl('^0CTS', I10_PR13)|
                                      grepl('^0CTS', I10_PR14)|
                                      grepl('^0CTS', I10_PR15)|
                                      grepl('^0CTS', I10_PR16)|
                                      grepl('^0CTS', I10_PR17)|
                                      grepl('^0CTS', I10_PR18)|
                                      grepl('^0CTS', I10_PR19)|
                                      grepl('^0CTS', I10_PR20)|
                                      grepl('^0CTS', I10_PR21)|
                                      grepl('^0CTS', I10_PR22)|
                                      grepl('^0CTS', I10_PR23)|
                                      grepl('^0CTS', I10_PR24)|
                                      grepl('^0CTS', I10_PR25))
```

```{r}
# filter 2019 with 0b11
filter_0B11_core_2019 <- core_2019 %>% filter(grepl('^0B11', I10_PR1)|grepl('^0B11', I10_PR2)|grepl('^0B11', I10_PR3)|
                                                grepl('^0B11', I10_PR4)|
                                                grepl('^0B11', I10_PR5)|
                                                grepl('^0B11', I10_PR6)|
                                                grepl('^0B11', I10_PR7)|
                                                grepl('^0B11', I10_PR8)|
                                                grepl('^0B11', I10_PR9)|
                                                grepl('^0B11', I10_PR10)|
                                                grepl('^0B11', I10_PR11)|
                                                grepl('^0B11', I10_PR12)|
                                                grepl('^0B11', I10_PR13)|
                                                grepl('^0B11', I10_PR14)|
                                                grepl('^0B11', I10_PR15)|
                                                grepl('^0B11', I10_PR16)|
                                                grepl('^0B11', I10_PR17)|
                                                grepl('^0B11', I10_PR18)|
                                                grepl('^0B11', I10_PR19)|
                                                grepl('^0B11', I10_PR20)|
                                                grepl('^0B11', I10_PR21)|
                                                grepl('^0B11', I10_PR22)|
                                                grepl('^0B11', I10_PR23)|
                                                grepl('^0B11', I10_PR24)|
                                                grepl('^0B11', I10_PR25))
```


```{r}
# filter core 2019 with 0cts
filter_0CTS_core_2019 <- core_2019 %>% filter(grepl('^0CTS', I10_PR1)|grepl('^0CTS', I10_PR2)|grepl('^0CTS', I10_PR3)|
                                                grepl('^0CTS', I10_PR4)|
                                                grepl('^0CTS', I10_PR5)|
                                                grepl('^0CTS', I10_PR6)|
                                                grepl('^0CTS', I10_PR7)|
                                                grepl('^0CTS', I10_PR8)|
                                                grepl('^0CTS', I10_PR9)|
                                                grepl('^0CTS', I10_PR10)|
                                                grepl('^0CTS', I10_PR11)|
                                                grepl('^0CTS', I10_PR12)|
                                                grepl('^0CTS', I10_PR13)|
                                                grepl('^0CTS', I10_PR14)|
                                                grepl('^0CTS', I10_PR15)|
                                                grepl('^0CTS', I10_PR16)|
                                                grepl('^0CTS', I10_PR17)|
                                                grepl('^0CTS', I10_PR18)|
                                                grepl('^0CTS', I10_PR19)|
                                                grepl('^0CTS', I10_PR20)|
                                                grepl('^0CTS', I10_PR21)|
                                                grepl('^0CTS', I10_PR22)|
                                                grepl('^0CTS', I10_PR23)|
                                                grepl('^0CTS', I10_PR24)|
                                                grepl('^0CTS', I10_PR25))
```

# filter out the patients died
```{r}
# core_2018_0B11 <- core_2018_0B11 %>%
#   filter(DIED == 0)
# core_2019_0B11 <- core_2019_0B11 %>%
#   filter(DIED == 0)
# 
# core_2018_0CTS <- core_2018_0CTS %>%
#   filter(DIED == 0)
# core_2019_0CTS <- core_2019_0CTS %>%
#   filter(DIED == 0)
```

# filter the patients have revisit 
```{r}
core_2018_0B11 <- core_2018_0B11 %>%
  filter(NRD_DaysToEvent>0) %>%
  group_by(NRD_VisitLink) %>%
  filter(n() > 1)

core_2019_0B11 <- core_2019_0B11 %>%
  filter(NRD_DaysToEvent>0) %>%
  group_by(NRD_VisitLink) %>%
  filter(n() > 1)

core_2018_0CTS <- core_2018_0CTS %>%
  filter(NRD_DaysToEvent>0) %>%
  group_by(NRD_VisitLink) %>%
  filter(n() > 1)

core_2019_0CTS <- core_2019_0CTS %>%
  filter(NRD_DaysToEvent>0) %>%
  group_by(NRD_VisitLink) %>%
  filter(n() > 1)
```



# extract the unique visit_link
```{r}
visit_link_0B112018 <- core_2018_0B11 %>%
  select(NRD_VisitLink, NRD_DaysToEvent,LOS)


revisit_0B112018 <- visit_link_0B112018 %>%
  group_by(NRD_VisitLink) %>%
  mutate(row_id = row_number()) %>%
  ungroup() %>%
  pivot_wider(
    names_from = row_id,
    values_from = c(NRD_DaysToEvent, LOS),
    names_sep = "_"
  )

```


```{r}
# Add new columns to the datase
revisit_0B112018$min_daystoevent <- NA
revisit_0B112018$max_daystoevent <- NA
revisit_0B112018$los_min <- NA
revisit_0B112018$los_max <- NA

# Find the day that patients first and second visit the hospital
for (i in 1:nrow(revisit_0B112018)) {
    

  days_list <- c(revisit_0B112018$NRD_DaysToEvent_1[i], revisit_0B112018$NRD_DaysToEvent_2[i], revisit_0B112018$NRD_DaysToEvent_3[i])

  los_list <- c(revisit_0B112018$LOS_1[i], revisit_0B112018$LOS_2[i], revisit_0B112018$LOS_3[i])
  

  valid_indices <- which(!is.na(days_list))
  

  valid_days <- days_list[valid_indices]
  valid_los <- los_list[valid_indices]
  

  sorted_indices <- order(valid_days)
  sorted_days <- valid_days[sorted_indices]
  sorted_los <- valid_los[sorted_indices]


  revisit_0B112018$min_daystoevent[i] <- sorted_days[1]
  revisit_0B112018$los_min[i] <- sorted_los[1]


  if (length(sorted_days) > 1) {
    revisit_0B112018$max_daystoevent[i] <- sorted_days[min(2, length(sorted_days))]
    revisit_0B112018$los_max[i] <- sorted_los[min(2, length(sorted_days))]
  }
}
```


# calculate the readmissiontime
```{r}
revisit_0B112018 <- revisit_0B112018 %>%
  mutate(revisit =  max_daystoevent - min_daystoevent - los_min)

```

# filter the revisit time that is within 30 days
```{r}
revisit_0B112018 <- revisit_0B112018 %>%
  filter(revisit < 31)
```


# left join
```{r}
select_cloums <- revisit_0B112018 %>%
  select(revisit, max_daystoevent,NRD_VisitLink)
core_2018_0B11 <- core_2018_0B11 %>%
  left_join(select_cloums, by = c("NRD_VisitLink" = "NRD_VisitLink", "NRD_DaysToEvent" = "max_daystoevent"))
```

# turn the revisit columns into binary variable
# 1 is revisit within 30 days, 0 is not revisit within 30 days
```{r}
core_2018_0B11 <- core_2018_0B11 %>%
  mutate(revisit = ifelse(!is.na(revisit), 1, 0))
```


# extract the unique visit_link
```{r}
visit_link_0B112019 <- core_2019_0B11 %>%
  select(NRD_VisitLink, NRD_DaysToEvent,LOS)


revisit_0B112019 <- visit_link_0B112019 %>%
  group_by(NRD_VisitLink) %>%
  mutate(row_id = row_number()) %>%
  ungroup() %>%
  pivot_wider(
    names_from = row_id,
    values_from = c(NRD_DaysToEvent, LOS),
    names_sep = "_"
  )

```


```{r}
revisit_0B112019$min_daystoevent <- NA
revisit_0B112019$max_daystoevent <- NA
revisit_0B112019$los_min <- NA
revisit_0B112019$los_max <- NA


for (i in 1:nrow(revisit_0B112019)) {

  days_list <- c(revisit_0B112019$NRD_DaysToEvent_1[i], revisit_0B112019$NRD_DaysToEvent_2[i], revisit_0B112019$NRD_DaysToEvent_3[i])
  los_list <- c(revisit_0B112019$LOS_1[i], revisit_0B112019$LOS_2[i], revisit_0B112019$LOS_3[i])
  
  valid_indices <- which(!is.na(days_list))
  valid_days <- days_list[valid_indices]
  valid_los <- los_list[valid_indices]


  sorted_indices <- order(valid_days)
  sorted_days <- valid_days[sorted_indices]
  sorted_los <- valid_los[sorted_indices]


  revisit_0B112019$min_daystoevent[i] <- sorted_days[1]
  revisit_0B112019$los_min[i] <- sorted_los[1]


  if (length(sorted_days) > 1) {
    revisit_0B112019$max_daystoevent[i] <- sorted_days[min(2, length(sorted_days))]
    revisit_0B112019$los_max[i] <- sorted_los[min(2, length(sorted_days))]
  }
}
```


# calculate the readmissiontime
```{r}
revisit_0B112019 <- revisit_0B112019 %>%
  mutate(revisit =  max_daystoevent - min_daystoevent - los_min)

```

# filter the revisit time that is within 30 days
```{r}
revisit_0B112019 <- revisit_0B112019 %>%
  filter(revisit < 31)
```


# left join
```{r}
select_cloums <- revisit_0B112019 %>%
  select(revisit, max_daystoevent,NRD_VisitLink)
core_2019_0B11 <- core_2019_0B11 %>%
  left_join(select_cloums, by = c("NRD_VisitLink" = "NRD_VisitLink", "NRD_DaysToEvent" = "max_daystoevent"))
```


```{r}
core_2019_0B11 <- core_2019_0B11 %>%
  filter(!(is.na(revisit)))
```

